A Multi-telescope Campaign on FRB 121102: Implications for the FRB Population

### 2017-07-26 repeater-vladata.tex
fixed spec index for proper effelsberg freq

Figure \ref{fig:multi} shows coarse spectra built from integrated flux densities measured (or limited) for the three VLA bursts with observing coverage by Arecibo or Effelsberg. The burst on MJD 57648 was detected with VLA and Arecibo with significances of 25$\sigma$\ and 39$\sigma$, which corresponds to peak flux densities in 5~ms of $111\pm5$\ mJy and $14\pm0.4$\ mJy at 3 and 1.4~GHz, respectively. The VLA observations under-resolve the pulses in time, so to compare these values, we assume a typical pulse width of 2~ms. Under this assumption, the VLA and Arecibo integrated flux densities are $278\pm13$\ and $57\pm2$\ mJy at 3 and 1.4~GHz, respectively. Assuming a power law flux density model ($S_{\nu} \propto \nu^{\alpha}$), we find a spectral index $\alpha=2.1$. This is inconsistent with the spectral index limit implied by the Effelsberg nondetection at 4.85~GHz ($\alpha<-1.7$\ for a 2~ms burst and $5\sigma$ limit).

Overall, the burst detections and nondetections show that burst spectra are not well described by a power-law model. Two Arecibo nondetections and two Effelsberg nondetections of VLA bursts place mutually inconsistent lower and upper limits on the spectral index. The Arecibo and Effelsberg upper limits at 1.4 and 4.85~GHz, respectively, limit all burst spectral indices $\alpha_{1.4/3}>+4.9$ and $\alpha_{3/4.85}<-2.7$. These are consistent with limits from the LWA1 and AMI-LA, which require $\alpha_{0.07/3}>-2.4$\ and $\alpha_{3/15}<1.5$ for bursts on MJD 57643 and 57649 (the brightest VLA bursts with observing coverage), respectively. The strictest limits on $\alpha_{1.4/3}$\ and $\alpha_{3/4.85}$\ are both derived from the burst on MJD 57649, which shows that a power law model is inappropriate even for a single burst.

>>>>

Figure \ref{fig:multi} shows coarse spectra built from integrated flux densities measured (or limited) for the three VLA bursts with observing coverage by Arecibo or Effelsberg. The burst on MJD 57648 was detected with VLA and Arecibo with significances of 25$\sigma$\ and 39$\sigma$, which corresponds to peak flux densities in 5~ms of $111\pm5$\ mJy and $14\pm0.4$\ mJy at 3 and 1.4~GHz, respectively. The VLA observations under-resolve the pulses in time, so to compare these values, we assume a typical pulse width of 2~ms. Under this assumption, the VLA and Arecibo integrated flux densities are $278\pm13$\ and $57\pm2$\ mJy at 3 and 1.4~GHz, respectively. Assuming a power law flux density model ($S_{\nu} \propto \nu^{\alpha}$), we find a spectral index $\alpha=2.1$. This is inconsistent with the spectral index limit implied by the Effelsberg nondetection at 4.85~GHz ($\alpha<-1.4$\ for a 2~ms burst and $5\sigma$ limit).

Overall, the burst detections and nondetections show that burst spectra are not well described by a power-law model. Two Arecibo nondetections and two Effelsberg nondetections of VLA bursts place mutually inconsistent lower and upper limits on the spectral index. The Arecibo and Effelsberg upper limits at 1.4 and 4.85~GHz, respectively, limit all burst spectral indices $\alpha_{1.4/3}>+4.9$ and $\alpha_{3/4.85}<-2.3$. These are consistent with limits from the LWA1 and AMI-LA, which require $\alpha_{0.07/3}>-2.4$\ and $\alpha_{3/15}<1.5$ for bursts on MJD 57643 and 57649 (the brightest VLA bursts with observing coverage), respectively. The strictest limits on $\alpha_{1.4/3}$\ and $\alpha_{3/4.85}$\ are both derived from the burst on MJD 57649, which shows that a power law model is inappropriate even for a single burst.
